\vspace{-15mm}\fontsize{16pt}{10pt}\selectfont\textbf{Facial Expression Recognition with\\ Convolutional Neural Networks}

### 2018-03-03 doc/paper.tex
ckplus elaborations

\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
\usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them

@@

\usepackage{titlesec} % Allows customization of titles
\usepackage[utf8]{inputenc}
\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

@@

Paul Ekmans 1969 research paper "Facial Expressions" elaborates that facial expressions can be interpreted as emotions. He suggests that there are six classes of basic emotion that can be found across all human cultures: anger, disgust, fear, happiness, sadness, and surprise. In this project, these classes are used as emotion classes for predictions.

For training an artificial neural network to classify facial expressions to these basic emotions, a dataset with labeled images of faces is required.

\subsection{FER-2013}
The FER-2013 Dataset consists of roughly 37.000 images showing faces of people expressing a certain emotion. Images are 48x48 pixel grayscale images of faces. These images have been centered automatically to show a similar region of the face in every sample.

Initially, the dataset is split into two subsets: A training set that is used to fit the prediction and a test set to evaluate the prediction results.

\begin{figure}[H]
	\includegraphics[width=0.48\textwidth]{class_dist}
	\caption{Class distribution across the training dataset}
\end{figure}

\subsection{Cohn-Kanade}

>>>>

\usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them

@@

\usepackage{titlesec} % Allows customization of titles
\usepackage[utf8]{inputenc}
%\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
%\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering\bfseries}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{}{\thesubsection.}{1em}{} % Change the look of the section titles

@@

Paul Ekmans 1969 research paper "Facial Expressions" elaborates that facial expressions can be interpreted and categorized into six classes of basic emotion that can be found across all human cultures: anger, disgust, fear, happiness, sadness, and surprise. In this project, these classes are used for training and predictions.

To build a classifier for facial expressions, a dataset with labeled images of faces is required. Each of the datasets is split into two subsets: A training set that is used to fit the prediction and a test set to evaluate the prediction results.

\subsection{FER-2013}

The FER-2013 Dataset consists of roughly 37.000 images showing faces of people expressing a certain emotion. Most of the 48x48 pixel grayscale images are stock footage. These images have been centered on the persons faces to show a similar region in every sample. As this has been done automatically, some images are not centered correctly. Faces are snapped from very different angles, hence generalization of these samples is difficult.

\begin{figure}[H]
	\includegraphics[width=0.48\textwidth]{class_dist}
	\caption{FER-2013 emotion class distribution}
\end{figure}

\subsection{Cohn-Kanade (CK+)}
To argument the wild variety of FER-2013 images, a second, more conservative dataset with only frontal faces is considered. CK+ consists of 593 image sequences across 123 subjects. Each image sequence goes from the neutral face to a "peak expression" according to the six basic emotions.
